---
title: "Untitled"
author: "Ismael Soto"
date: "10/2/2023"
output: html_document
---

## Just to be sure that the methodology is correct: 
# The experiment set up is:
3 crayfish: "G", "N" and "E".
Length: 16-21 mm

#Summary of the experiment (1)
We evaluate the consumption rate of crayfish under six levels of prey density: (1, 3, 6, 12, 18)

```{r}
suppressMessages({
  library(dplyr, quiet = TRUE, warn.conflicts = FALSE)
  library(reshape, quiet = TRUE, warn.conflicts = FALSE)
  library(ggplot2)
  library(stringr)
  library(tidyr)  
  library(stringr)
  library(readxl)
  library(frair)
  library(patchwork)
  library(glmmTMB)
})
```

```{r}
setwd("C:/Users/isma-/OneDrive/Escritorio/Tonda")
df <- read_excel("Tonda_student.xlsx", sheet = "Ismael")
```

```{r}
df[is.na(df)] <- 0
```
```{r}
df1<- df[,c(1:11)] #Group Non-reproductive
df2<- df[,c(2,12:20)] #Group Glands
df3<- df[,c(2,21:29)] #Group Eggs
```


```{r}
frair_test(formula = Total  ~  `Prey density` , data = df1) 
```

```{r}
frair_test(formula = Total1  ~  `Prey density` , data = df2)
```


```{r}
frair_test(formula = Total2  ~  `Prey density` , data = df3) 
```

## Result
All the crayfish groups follows a type-II response

Example: https://en.wikipedia.org/wiki/Functional_response



#Functional response analyse
#a: attack rate
#h: handling time
#T: time exp
```{r }
g_fit1 <- frair_fit(formula = Total ~ `Prey density`, data = df1,
                   response = "rogersII",
                   start = list(a = 1, h = 0.1),
                   fixed = list(T = 1)) 
with(df1, plot(`Prey density`, Total, xlab="Prey Density",
                    ylab="No. Prey Eaten"))
lines(g_fit1, lty = 1, col = "grey25")
print(g_fit1)
summary(g_fit1$fit)
```



```{r }
g_fit2 <- frair_fit(formula = Total1 ~ `Prey density`, data = df2,
                   response = "rogersII",
                   start = list(a = 1, h = 0.1),
                   fixed = list(T = 1)) #days
with(df2, plot(`Prey density`, Total1, xlab="Prey Density",
                    ylab="No. Prey Eaten"))
lines(g_fit2, lty = 1, col = "grey55")
print(g_fit2)
summary(g_fit2$fit)
```

```{r}
g_fit3 <- frair_fit(formula = Total2 ~ `Prey density`, data = df3,
                   response = "rogersII",
                   start = list(a = 1, h = 0.1),
                   fixed = list(T = 1)) #days
with(df3, plot(`Prey density`, Total2, xlab="Prey Density",
                    ylab="No. Prey Eaten"))
lines(g_fit3, lty = 1, col = "grey55")
print(g_fit3)
summary(g_fit3$fit)
```

```{r}
fitp_fit1 <- frair_boot(g_fit1)
confint(fitp_fit1 , citypes ='bca')
```

```{r}
fitp_fit2 <- frair_boot(g_fit2)
confint(fitp_fit2 , citypes ='bca')
```

```{r}
fitp_fit3 <- frair_boot(g_fit3)
confint(fitp_fit3 , citypes ='bca')
```

## PLOT
```{r}
#svg("Figure1.svg")
plot(x = 1,
     type = "n",
     xlim = c(0, 26), 
     ylim = c(0, 20),
     xlab="Prey Density", ylab="No. of prey killed")


drawpoly(fitp_fit1, col=("royalblue1"), border=NA, tozero=TRUE)
drawpoly(fitp_fit2, col=("palegreen2"), border=NA, tozero=TRUE)
drawpoly(fitp_fit3, col=("orangered1"), border=NA, tozero=TRUE)

points(x = df2$`Prey density`, y = df2$Total1, pch="+", cex=0.9, col= "palegreen2",alpha = 0.5)
points(x = df3$`Prey density`, y = df3$Total2, pch="x", cex=0.7, col= "orangered1",alpha = 0.5)
points(x = df1$`Prey density`, y = df1$Total, pch="*", cex=0.9, col = "royalblue1",alpha = 0.5)

lines(g_fit1, col = "royalblue1", lty=1, lwd=3) ##Group Non-reproductive
lines(g_fit2, col = "palegreen2",lty=2,  lwd=3 ) #Glands
lines(g_fit3, col = "orangered1",lty=3,  lwd=3 ) #Eggs

legend(1, 19, legend=c("No reproductive", "Glair glands","Eggs"),
       col=c("royalblue1", "palegreen2","orangered1"), lty=1:2, cex=0.8)

dev.off()
```


### Check the attack rate (a) and handling time (h) through error bars from bootstraps

```{r}
########### Ahora plot boxplots

a<- fitp_fit1$bootcoefs %>% as.data.frame() %>% mutate(Lower="2.883",
                                                       Upper="8.81",
                                                       point="4.600") 
a$Clawless <- "No reproductive"
b<- fitp_fit2$bootcoefs %>% as.data.frame()%>% mutate(Lower="1.372",
                                                      Upper="4.322",
                                                      point="2.447")
b$Clawless <- "Glair glands"
c<- fitp_fit3$bootcoefs %>% as.data.frame()%>% mutate(Lower="0.25",
                                                      Upper="7.863",
                                                      point="1.044")
c$Clawless <- "Eggs"

df<- bind_rows(a,b,c)
str(df)

str(df)
df$Lower<- as.numeric(df$Lower)
df$Upper<- as.numeric(df$Upper)
df$point<- as.numeric(df$point)

df$Clawless <- factor(df$Clawless, 
          levels = c("No reproductive","Glair glands","Eggs"))

df <- df[!duplicated(df$Clawless),]

#svg("p1.svg")
p<- ggplot(df, aes(Clawless,a,colour = Clawless)) 
p1<- p + geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2) +theme_bw() + ylab("Attack rate (± SE)")+
  ylim(0,10)+ geom_point(data=df,aes(Clawless,point)) +xlab("")
p1
dev.off()
```

```{r}
d<- fitp_fit1$bootcoefs %>% as.data.frame() %>% mutate(Lower="0.101",
                                                       Upper="0.146",
                                                       point="0.121") 
d$Clawless <- "No reproductive"
e<- fitp_fit2$bootcoefs %>% as.data.frame()%>% mutate(Lower="0.164",
                                                      Upper="0.281",
                                                      point="0.224")
e$Clawless <- "Glair glands"
f<- fitp_fit3$bootcoefs %>% as.data.frame()%>% mutate(Lower="0.482",
                                                      Upper="1.145",
                                                      point="0.764")
f$Clawless <- "Eggs"

df1<- bind_rows(d,e,f)
str(df1)

str(df1)
df1$Lower<- as.numeric(df1$Lower)
df1$Upper<- as.numeric(df1$Upper)
df1$point<- as.numeric(df1$point)

df1$Clawless <- factor(df1$Clawless, 
          levels = c("No reproductive","Glair glands","Eggs"))

df1 <- df1[!duplicated(df1$Clawless),]


svg("p2.svg")
p<- ggplot(df1, aes(Clawless,h,colour = Clawless)) 
p2<-p + geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.2) +theme_bw() + 
  ylab("Handling time (± SE)") + geom_point(data=df,aes(Clawless,point))+ylim(0,1.2)+
  xlab("")

p2
dev.off()
```

```{r}
p1+p2
```

## Partial consumption of prey


```{r}
setwd("C:/Users/isma-/OneDrive/Escritorio/Tonda")
df <- read_excel("Tonda_student.xlsx", sheet = "Ismael")
head(df)
```


```{r}
df[is.na(df)] <- 0
```

```{r}
df1<- df[,c(1:10)] #Group Non-reproductive
df1 <- df1[,-1]
df2<- df[,c(2,11:18)] #Group eggs
df3<- df[,c(2,19:26)] #Group glands
```

```{r}
names<- colnames(df1)
colnames(df2)<- names
colnames(df3)<- names
```


```{r}
df<- rbind(df1,df2,df3)
```


```{r}
colnames(df)
colnames(df) <- c("Prey density","Code","Alive","1","0.75","0.5","0.25","0","Total")

df<- df %>% pivot_longer(!c(Code,`Prey density`,`1`,`0`, Alive, Total), 
                         names_to = "Partial_consumend", values_to = "Partial")


df$Code <- as.factor(df$Code)
head(df)
```


```{r}
df$all_consumed <- df$`1` + df$`0`


### Zero inflated because there are mannnnnnnnnnnny 0 (more than expected)
head(df)
str(df)
hist(df$Partial)
```

```{r}
model1 <- glmmTMB(cbind(Partial, all_consumed) ~ Code*`Prey density`, ziformula = ~1,
                  data = df, family = binomial(link = "logit"))

summary(model1)

```

```{r}
library(car)
result<-car::Anova(model1, Type=3)
result

library(lsmeans)
lsmeans(model1,pairwise~Code,data=df) 
```

## :DD
```{r}
setwd("C:/Users/isma-/OneDrive/Escritorio/Tonda")
df <- read_excel("Tonda_student.xlsx", sheet = "Sheet4")
head(df)
```

```{r}
svg("Figure3.svg")
ggplot(df,  aes(x = Prey_density, y = Average, ymin = Average-SD, ymax = Average+SD))+
 geom_pointrange(aes(color = Group), position = position_dodge(width = 2)) + theme_bw()+ ylab("Prey partially consumed") +
  scale_x_discrete(name ="Prey density", 
                    limits=c("1","3","6","12","18","24"))
dev.off()
```


